\Large \bf Dynamic Program Dialysis with Lya

### 2020-01-11 paper/draft.tex
Dismantling

\begin{figure}[t]
\raggedleft 
\includegraphics[width=0.45\textwidth]{./figs/lya_base.pdf}
\caption{
  \textbf{Base transformation.}
  \textmd{
  The algorithm (simplified) is presented in functional style to simplify variable binding; types (object, list, function, and primitive), used for pattern matching, are shown in light {\color{cdb} \emph{turquoise}}~\cf{bt}.
  }
}
\label{fig:base}
\end{figure}

The program transformations described earlier~\sx{overview} are in \sys  abstracted by a set of parametrizable skeletons.
These skeletons provide hooks for end-developers writing analyses.
Specifically, they map types of values (\eg \ttt{Number}s, \ttt{Function}s) to generic hooks for each type. 
These hooks are then extended or rewritten by developers to

For example, consider transforming a \ttt{Math} object with the goal of profiling its interfaces or generating a remote interface (Fig.~\ref{fig:lib}\emph{a,b}).
\sys traverses the object returned by \ttt{Math} and replaces functions such as \ttt{div} with wrappers.
The wrappers depend on the intended goal:
  profiling wrappers would record invocation statistics, and RPC wrappers would forward calls to a remote replica.

\subsection{Disassembly}
\label{one}

>>>>

\begin{figure}[t]
\raggedleft 
\includegraphics[width=0.45\textwidth]{./figs/lya_base.pdf}
\caption{
  \textbf{Base transformation.}
  \textmd{
  The algorithm (simplified) is presented in functional style to simplify variable binding; types (object, list, function, and primitive), used for pattern matching, are shown in light {\color{cdb} \emph{turquoise}}~\cf{bt}. The meta-function $\alpha$ stands for the locations of analysis hooks.
  }
}
\label{fig:base}
\end{figure}

% To transform a module, \sys augments several steps of the module loading process (Fig.~\ref{fig:pipeline}) using a base transformation that wraps an object with a security monitor~\sx{bt}.
% It starts by intercepting calls to the \ttt{require} function~\sx{import}, which locates the module's source code and \pc.
% It then constructs a custom context based on the \pc's implicit segment~\sx{context}.
% It then encloses the module in a closure to leverage local variable resolution in order to link the custom context with the module~\sx{enclosure}.
% After source interpretation, \sys transforms the resulting value by consulting the \pc's explicit segment~\sx{final}, updates the \sys-augmented module cache~\sx{cache}, and returns the value to the consumer.
% The following subsections detail these steps.

\subsection{Dismantling}
\label{one}

When the dialysis starts along with the rest of the program, it first loads the analysis hooks provided by the developer. 
Among other things, \sys needs to determine which library boundaries are of interest and what the granularity of the analysis is going to be.
For the former, developers may have specified a subset of libraries whose boundaries are of interest or a subset of libraries that should \emph{not} be analyzed.
For the latter, it checks the constructs that---for example, whether the analysis includes global variables, library-local constructs, standard libraries \etc

It then dynamically replaces the implementation of\ttt{import}:
  rather than simply locating and loading a library, the function yields to \sys.

\sys checks the cache~\sx{three} to determine (i) if the library has already been loaded, and (ii) whether it has been loaded with the same analysis hooks.
If both are determined true, \sys retrieves the cached version of the library and returns the transformed \ttt{export}ed value.
If the library was loaded with a different analysis---say because there are different analyses applied to different parts of a dependency tree---\sys constructs the appropriate analysis and applies a transformation pass on a cached copy of the unmodified library~\sx{three}.
% \omit{---the common case---}
Otherwise, \sys first invokes the built-in library loader to locate the library.

The process of loading new libraries includes (i) a phase of reading the necessary files as source code and (ii) a phase of interpreting them, interspersed by applications of transformations.
Reading files returns a string representation of the code; interpretation uses the language's runtime evaluation primitives to convert the code to an in-memory object.
A series of transformations is applied before and after interpretation~\sx{two}.

Some analyses may themselves make use of global variables, libraries, and other analyzable constructs.
\sys must note not to include these constructs in the ones 
% The analysis language is embedded in the source language, thus \sys makes use of the language's built-in evaluation primitives to interpret the \pc specification file.
Dialysis frameworks may want to add analysis-specific keywords not provided by the language.
To achieve this, \fixme{we} wrap each analysis hook with a function whose body starts by defining the expected keywords.
The precise techniques for achieving this will be made clear in the next section~\sx{two}, after covering transformations;
  the key to remember is that analysis are loaded from disk as source files, similar to libraries.
